---
title: "STACK responses - analysis of coding"
author: "George Kinnear"
date: "2022-03-07"
always_allow_html: true
output:
  html_document:
    df_print: paged
    toc: true
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)

# Tables
library(knitr)
library(kableExtra)
basic_kable = function(df) {
  df %>% 
    kable() %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}
rmarkdown::html_document(df_print = knitr::kable)
options(knitr.kable.NA = '')

# Set preferred styling
theme_set(theme_minimal())
```

```{r}
files <- fs::dir_ls(path = "2020-stack-responses/", glob = "*attempts_q*csv")
response_data_raw <- vroom::vroom(files, id = "csv_path")#, show_col_types = FALSE)

response_data <- response_data_raw %>% 
  filter(!userid %in% c(2)) %>% 
  # identify the question part a/b/c/d
  mutate(question = str_extract(csv_path, "attempts_q([:digit:])") %>% parse_number()) %>% 
  mutate(part = letters[question], .before = 1, .keep = "unused") %>% 
  # keep only the relevant columns
  select(part, responsesummary, state, fraction, userid) %>% 
  # pick out the bits of the responsesummary
  extract(responsesummary, into = c("response", "score", "prt"), regex = ".*ans1: ([^\\| ]*) \\[score\\]; prt1: # = ([^\\| ]*) \\| (.*)") %>% 
  mutate(score = parse_number(score))
```

## Response summary

There are two issues with the responses that complicate the analysis:

1.  STACK offered partial credit for parts b/c/d, and
2.  students did not always give a response; these are shown as a score of `NA` rather than a score of 0.

```{r}
response_data %>%
  group_by(part, score) %>% 
  tally()
```

```{r}
correctness_summary <- response_data %>%
  # correct only when the score is 1, incorrect otherwise
  #mutate(correct = if_else(!is.na(score), score == 1, FALSE)) %>% 
  mutate(correct = if_else(!is.na(score), score == 1, NA)) %>% 
  group_by(part, correct) %>% 
  tally()

correctness_summary %>%
  pivot_wider(names_from = "correct", values_from = "n") %>%
  rename(Part = part, Correct = `TRUE`, Incorrect = `FALSE`) %>% 
  rowwise() %>% 
  mutate(Total = sum(Correct, Incorrect)) %>% 
  basic_kable()

correctness_summary2 <- response_data %>%
  # correct only when the score is 1, incorrect otherwise
  mutate(correct = if_else(!is.na(score) & score == 1, "Correct", "Incorrect")) %>%
  # correct only when the score is 1, incorrect otherwise, except if no response
  mutate(correct = case_when(
    is.na(score) ~ "No response",
    score == 1 ~ "Correct",
    TRUE ~ "Incorrect"
  )) %>%
  janitor::tabyl(part, correct)

correctness_summary2 %>%
  janitor::adorn_totals("col") %>%
  janitor::adorn_percentages() %>%
  janitor::adorn_pct_formatting(digits = 0) %>%
  janitor::adorn_ns(position = "front") %>% 
  basic_kable()
  
correctness_summary2 %>% 
  pivot_longer(cols = !part, names_to = "correct", values_to = "n") %>% 
  mutate(correct = fct_rev(correct)) %>% 
  ggplot(aes(x = part, y = n, group = correct, fill = correct)) +
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_viridis_d(option = "plasma", end = 0.8) +
  labs(title = "Number of correct answers to each part")
```

## Response details

(Here, all "null" responses are discarded rather than being counted as incorrect.)

Looking in more detail at the specific questions:

```{r}
coord_names = paste0(c("x", "y"), ceiling(c(1:8)/2))
response_coords = response_data %>%
  mutate(ans_nums = str_replace_all(response, "\\[|\\]", "")) %>% 
  filter(!is.na(score)) %>% 
  separate(ans_nums, into = coord_names, sep = ",", remove = FALSE) %>% 
  mutate(across(all_of(coord_names), as.numeric))

response_coords %>% 
  pivot_longer(cols = all_of(coord_names), names_to = "coord", values_to = "value") %>% 
  separate(coord, into = c("coord", "pt_num"), sep = 1) %>% 
  pivot_wider(names_from = "coord", values_from = "value") %>% 
  ggplot(aes(x = x, y = y, group = userid, colour = userid)) +
  facet_grid(rows = vars(part), cols = vars(score)) +
  geom_point() +
  geom_line() +
  theme(legend.position = "none")

```

## Check for specific issues in answers

```{r}
response_issues <- response_coords %>% 
  rowwise() %>% 
  mutate(
    image_min = min(c(y1, y2, y3, y4)),
    image_max = max(c(y1, y2, y3, y4)),
    domain_min = min(c(x1, x2, x3, x4)),
    domain_max = max(c(x1, x2, x3, x4))
  ) %>% 
  mutate(
    # some students seemed to place the points on top of each other
    has_repeated_pt = case_when(
      x1 == x2 & y1 == y2 ~ TRUE,
      x3 == x2 & y3 == y2 ~ TRUE,
      x3 == x4 & y3 == y4 ~ TRUE
    ),
    example_type = case_when(
      length(unique(c(x1,x2,x3,x4))) < 4 ~ "not a function",
      TRUE ~ "piecewise linear"
    ),
    null_response = if_else(all(c(x1,x2,x3,x4) == c(0, 0.3, 0.7, 1)) && all(c(y1,y2,y3,y4) == c(0,0,0,0)), "No response", NA_character_),
    nature_of_mistake_domain = case_when(
      domain_min == 0 & domain_max == 0.5 ~ "domain is [0,1/2]",
      domain_min < 0 | domain_max > 1 ~ "domain exceeds [0,1]", # should not be possible, given the interface!
      domain_min > 0 | domain_max < 1 ~ "domain has gaps",
    ),
    nature_of_mistake_image = case_when(
      image_min < 0 | image_max > 1 ~ "image goes beyond [0,1]",
      
      # for a, the image should be [0,1/2]
      part == "a" & image_min == 0.5 & image_max == 1 ~ "image is [1/2,1]",
      part == "a" & image_min == 0 & image_max == 1 ~ "surjective but should not be",
      
      # for b, the image should be [0,1/2]
      part == "b" & (image_max < 0.5) ~ "image too small",
      part == "b" & image_max > 0.5 & image_min == 0 ~ "image too large",
      part == "b" & image_max != 0.5 & image_min != 0 ~ "image other",
      
      # for c, the image should be [0,1]
      part == "c" & image_min == 00 & image_max == 0.5 ~ "image is [0,1/2]",
      part == "c" & (image_min > 0 | image_max < 1) ~ "image too small",
      
      # for d, the image should be smaller than [0,1]
      part == "d" & image_min == 0 & image_max == 1 ~ "surjective but should not be",
    ),
    nature_of_mistake_other = case_when(
      (part == "b" | part == "c") & (all(diff(c(y1,y2,y3,y4)) > 0) | all(diff(c(y1,y2,y3,y4)) < 0)) ~ "injective but should not be",
    )
  ) %>% 
  mutate(nature_of_mistake = paste0(na.omit(c(null_response, nature_of_mistake_domain, nature_of_mistake_image, nature_of_mistake_other)), collapse = "; "))

response_issues %>% group_by(part, score, example_type, nature_of_mistake) %>% tally() %>% basic_kable()
```


```{r}
plot_responses <- function(responses_to_plot, title = "Responses") {
  responses_to_plot %>% 
    pivot_longer(cols = all_of(coord_names), names_to = "coord", values_to = "value") %>% 
    separate(coord, into = c("coord", "pt_num"), sep = 1) %>% 
    pivot_wider(names_from = "coord", values_from = "value") %>% 
    ggplot(aes(x = x, y = y)) +
    facet_wrap(vars(userid)) +
    geom_point(colour = "#003399") +
    geom_line(colour = "#003399") +
    #geom_label(data = responses_to_plot, aes(x = 0, y = Inf, label = nature_of_mistake), hjust = 0) +
    coord_cartesian(ylim = c(0, 1), xlim = c(0, 1), clip = "off") +
    scale_y_continuous(breaks = seq(0, 1, 1), minor_breaks = seq(0, 1, 0.1)) +
    scale_x_continuous(breaks = seq(0, 1, 1), minor_breaks = seq(0, 1, 0.1)) +
    theme(legend.position = "none") +
    theme(panel.spacing = unit(2, "lines")) +
    theme(aspect.ratio = 1) +
    labs(title = title, x = "", y = "")
}
```


### (a) image $[0,\frac12]$

```{r}
response_issues %>%
  filter(part == "a") %>%
  group_by(score, example_type, nature_of_mistake) %>%
  tally() %>%
  arrange(-score, example_type, -n) %>% 
  basic_kable() %>% 
  collapse_rows(columns = c(1:2), valign = "top")
```

#### Correct answers

```{r}
part_a_correct <- response_issues %>% 
  filter(part == "a", score == 1) %>% 
  mutate(part_a_type = case_when(
    all(c(y1-x1/2, y2-x2/2, y3-x3/2, y4-x4/2) == 0) ~ "1. y = x/2",
    y1 < y2 && y2 < y3 && y3 < y4 ~ "2. increasing",
    y1 == 0 & y1 < y2 && y3 > y4 && y4 ==0 ~ "3. hump / peak / valley",
    y1 == 0.5 & y1 > y2 && y3 < y4 && y4 ==0.5 ~ "3. hump / peak / valley",
    length(which(c(y1,y2,y3,y4) != 0)) == 1 ~ "4. only one point moved",
    #y1 < y2 && y2 > y3 && y3 < y4 ~ "x. zig zag",
    TRUE ~ "other",
  )) %>% 
  group_by(part_a_type) %>% 
  mutate(count = n())

part_a_correct %>% 
  group_by(part_a_type) %>% 
  slice_head(n = 1) %>% 
  mutate(userid = str_glue("{part_a_type} (n={count})")) %>% 
  plot_responses(title = "Families of correct responses")

ggsave("2020-stack-responses/FIG_task1_correct.pdf", units = "cm", width = 18)

part_a_correct %>% 
  filter(part_a_type == "other") %>% 
  plot_responses(title = "Responses in the \"other\" category")
```

How often did students realise they could move the points horizontally?

```{r}
part_a_correct %>% 
  group_by(part_a_type, x1, x2, x3, x4) %>% 
  tally()
```

Most of the "increasing" examples (64 of the 84) used the default x-coordinates.

#### Not a function

Several students gave responses with vertical segments.

Apparent among these are several students joining the points (0,1) and (0,1/2), perhaps confusing the interval notation in the question for coordinates of points?

```{r fig.height=7, fig.width=8}
response_issues %>% 
  filter(part == "a", score == 0, example_type == "not a function") %>% 
  plot_responses(title = "Not a function, score = 0")
```

Some of these responses are close to correct, in the sense that minor perturbation of one of the points would make a vertical segment merely very steep, and the function would have the required properties (e.g. `userid` 2900, 3400, 3407).

There were a few students who made some of the points overlap, but ignoring the duplicates, the resulting graph is correct:

```{r fig.height=3, fig.width=8}
response_issues %>% 
  filter(part == "a", score == 1, example_type == "not a function") %>% 
  plot_responses(title = "Not a function, score = 1")
```

#### Piecewise linear

Among students who correctly plotted a piecewise linear function, there were a few common mistakes.

##### 1. Surjective but should not be

```{r fig.height=5, fig.width=8}
response_issues %>% 
  filter(part == "a", score != 1, example_type != "not a function", nature_of_mistake_image == "surjective but should not be") %>% 
  plot_responses(title = "surjective but should not be, score < 1")
```
	
Out of these, there are only 5 cases where the student has given an example with a domain of $[0,\frac12]$, consistent with confusing the domain and image.

The rest seem to just be ignoring the condition on the image.

##### 2. Confusing domain and image?

Another other common issue was for students to give an example with domain $[0,\frac12]$:

```{r fig.height=4, fig.width=8}
response_issues %>% 
  filter(part == "a", score != 1, example_type != "not a function", nature_of_mistake_domain == "domain is [0,1/2]") %>% 
  plot_responses(title = "Domain is [0,1/2], score < 1")
```

In many of these examples, the image is also $[0,\frac12]$ (e.g. `userid` 4151).


##### 3. Gaps in the domain

Many students used some other subset of $[0,1]$ as the domain, only sometimes with the correct image:

```{r fig.height=4, fig.width=8}
response_issues %>% 
  filter(part == "a", score != 1, example_type != "not a function", nature_of_mistake_domain == "domain has gaps") %>% 
  plot_responses(title = "Domain has gaps, score < 1")
```

##### 4. Miscellaneous

Finally, there were several students giving responses that were incorrect, but did not fit any of the previously defined categories.

There are perhaps two identifiable "families" among these:

1. constant functions (e.g. `userid` 2741)
2. almost correct answers, perhaps let down by poor scale reading? (e.g. `userid` 2695, where the highest values are close to, but just below, 0.5; or `userid` 3281 which overshoots 0.5 at the right endpoint.)

```{r fig.height=7, fig.width=8}
response_issues %>% 
  filter(part == "a", score != 1, example_type != "not a function", nature_of_mistake == "") %>% 
  plot_responses(title = "Unknown error")
```


### (b) image $[0,\frac12]$ and not injective

```{r}
response_issues %>%
  filter(part == "b") %>%
  group_by(score, example_type, nature_of_mistake) %>%
  tally() %>%
  arrange(-score, example_type, -n) %>% 
  basic_kable() %>% 
  collapse_rows(columns = c(1:2), valign = "top")
```

#### Correct answers

```{r}
part_b_correct_old_classification <- response_issues %>% 
  filter(part == "b", score == 1) %>% 
  mutate(part_b_type = case_when(
    y1 == 0 & y2 == 0.5 && y3 == 0.5 && y4 ==0 ~ "1. hump",
    y1 == y2 | y2 == y3 | y3 == y4 ~ "2. flat part",
    y1 < y2 && y2 > y3 && y3 < y4 ~ "3. zig zag",
    y1 < y2 && y2 > y3 && y3 > y4 ~ "4. concave down",
    y1 < y2 && y2 < y3 && y3 > y4 ~ "4. concave down",
    TRUE ~ "other"
  )) %>% 
  group_by(part_b_type) %>% 
  mutate(count = n())

part_b_correct_old_classification %>% 
  filter(part_b_type == "2. flat part") %>% 
  head(n = 16) %>% 
  plot_responses()

part_b_correct <- response_issues %>% 
  filter(part == "b", score == 1) %>% 
  mutate(part_b_type = case_when(
    y1 == 0 && y2 == 0.5 && y3 == 0.5 && y4 == 0 ~ "1. hump - down",
    y1 == 0.5 && y2 == 0 && y3 == 0 && y4 == 0.5 ~ "1. hump - up",
    y1 <= y2 && y2 <= y3 && y3 <= y4 ~ "2. nondecreasing",
    y1 >= y2 && y2 >= y3 && y3 >= y4 ~ "X. nonincreasing",
    y1 < y2 && y2 > y3 && y3 < y4 ~ "3. zig zag",
    y1 > y2 && y2 < y3 && y3 > y4 ~ "3. zig zag",
    y1 == 0 && y4 == 0 ~ "4. hump - other",
    y1 <= y2 && y3 >= y4 ~ "4. hump - other",
    y1 == 0.5 && y4 == 0.5 ~ "4. hump - other",
    y1 >= y2 && y3 < y4 ~ "4. hump - other",
    TRUE ~ "other"
  )) %>% 
  group_by(part_b_type) %>% 
  mutate(count = n())

part_b_correct %>% 
  group_by(part_b_type) %>% 
  slice_head(n = 1) %>% 
  mutate(userid = str_glue("{part_b_type} (n={count})")) %>% 
  plot_responses(title = "Task B: Families of correct responses")

ggsave("2020-stack-responses/FIG_task2_correct.pdf", units = "cm", width = 18)
```

```{r fig.height=7, fig.width=8}
part_b_correct %>% 
  filter(str_detect(part_b_type, "1. hump")) %>% 
  head(n = 25) %>% 
  plot_responses("Task B: humps of both types (first 25)") + theme(panel.spacing = unit(0.2, "lines"))


part_b_correct %>% 
  filter(part_b_type == "2. nondecreasing") %>% 
  plot_responses("Task B: nondecreasing") + theme(panel.spacing = unit(0.2, "lines"))

part_b_correct %>% 
  filter(part_b_type == "3. zig zag") %>% 
  plot_responses("Task B: zig-zag") + theme(panel.spacing = unit(0.2, "lines"))

part_b_correct %>% 
  filter(part_b_type == "4. hump - other") %>% 
  plot_responses("Task B: hump-other") + theme(panel.spacing = unit(0.2, "lines"))


```


#### Not a function

Within the examples that are "not a function", some of them had unidentified mistakes. This is either because they use vertical segments, or because two points have been dragged to coincide.

```{r fig.height=7, fig.width=8}
response_issues %>% 
  filter(part == "b", score == 0, nature_of_mistake == "") %>% 
  plot_responses(title = "Not a function")
```

The remaining "not a function" responses are quite varied:

```{r fig.height=7, fig.width=8}
response_issues %>% 
  filter(part == "b", score == 0, example_type == "not a function", nature_of_mistake != "") %>% 
  plot_responses(title = "Not a function")
```

#### Partially correct

```{r fig.height=4, fig.width=8}
response_issues %>% 
  filter(part == "b", score == 0.5, nature_of_mistake == "image too small") %>% 
  plot_responses(title = "Image too small")
```

```{r fig.height=4, fig.width=8}
response_issues %>% 
  filter(part == "b", score == 0.5, nature_of_mistake == "image too large") %>% 
  plot_responses(title = "Image too large")
```

```{r fig.height=2, fig.width=8}
response_issues %>% 
  filter(part == "b", score == 0.5, nature_of_mistake == "injective but should not be") %>% 
  plot_responses(title = "Injective but should not be")
```

#### Incorrect

```{r fig.height=5, fig.width=8}
response_issues %>% 
  filter(part == "b", score == 0, example_type == "piecewise linear", str_detect(nature_of_mistake, "image too small")) %>% 
  plot_responses(title = "Image too small")
```

Several of those are horizontal lines.


```{r}
part_b_mistakes <- response_issues %>% 
  filter(part == "b") %>% 
  mutate(mistake = case_when(
    !is.na(nature_of_mistake_domain) && !is.na(nature_of_mistake_image) ~ "both",
    !is.na(nature_of_mistake_domain) ~ "domain",
    !is.na(nature_of_mistake_image) ~ "image",
    str_length(nature_of_mistake) > 0 ~ "other",
    example_type == "not a function" ~ "other",
    TRUE ~ "none"
  ))

part_b_mistakes %>% 
  count(mistake)

part_b_mistakes %>% 
  janitor::tabyl(mistake) %>% 
  filter(mistake != "none") %>% 
  mutate(mistake = fct_relevel(as.factor(mistake), "domain", "both", "image", "other")) %>% 
  ggplot(aes(x = 1, y = n, fill = mistake)) +
  geom_bar(position = "stack", stat = "identity") +
  coord_flip()
```

```{r fig.height=5, fig.width=8}
part_b_mistakes %>% 
  group_by(mistake, nature_of_mistake_domain, nature_of_mistake_image) %>% 
  tally()

part_b_mistakes %>% 
  filter(mistake == "both") %>% 
  plot_responses(title = "Wrong image and domain")


```

Just the point (0, 1/2) - one student does this for both (a) and (b); there are two other students doing it for (a), and two separate students for (b).

```{r}
response_issues %>% 
  filter(x1 == 0, x2 == 0, x3 == 0, x4 == 0, y1 == 0.5, y2 == 0.5, y3 == 0.5, y4 == 0.5)
```



```{r fig.height=5, fig.width=8}
response_issues %>% 
  filter(part == "b", score == 0, example_type == "piecewise linear", str_detect(nature_of_mistake, "domain")) %>% 
  plot_responses(title = "Problem with the domain")
```


```{r fig.height=5, fig.width=8}
response_issues %>% 
  filter(part == "b", score == 0, example_type == "piecewise linear", str_detect(nature_of_mistake, "injective")) %>% 
  plot_responses(title = "Injective but should not be")
```






### (c) surjective and not injective

```{r}
response_issues %>%
  filter(part == "c") %>%
  group_by(score, example_type, nature_of_mistake) %>%
  tally() %>%
  arrange(-score, example_type, -n) %>% 
  basic_kable() %>% 
  collapse_rows(columns = c(1:2), valign = "top")
```

#### Correct answers

To get a feel for the range of responses, we first analyse based on the slopes of the three segments:


```{r, fig.height=6, fig.width=6}
incdecanalysis <- function(y1, y2, y3, y4) {
  seg1 <- ifelse(y2 > y1, "inc", ifelse(y2 == y1, "flat", "dec"))
  seg2 <- ifelse(y3 > y2, "inc", ifelse(y3 == y2, "flat", "dec"))
  seg3 <- ifelse(y4 > y3, "inc", ifelse(y4 == y3, "flat", "dec"))
  return(paste(seg1, seg2, seg3))
}

response_issues %>% 
  filter(part == "c", score == 1) %>% 
  mutate(example_type = pmap_chr(list(y1,y2,y3,y4), incdecanalysis)) %>% 
  group_by(example_type) %>% 
  mutate(count = n()) %>% 
  slice_head(n = 1) %>% 
  mutate(userid = str_glue("{example_type} (n={count})")) %>% 
  ungroup() %>% 
  mutate(userid = fct_reorder(userid, -count)) %>% 
  plot_responses(title = "Task C: Responses grouped by segment slopes")
```

```{r}
part_c_correct <- response_issues %>% 
  filter(part == "c", score == 1) %>% 
  mutate(incdec = pmap_chr(list(y1,y2,y3,y4), incdecanalysis)) %>% 
  mutate(part_c_type = case_when(
    all(diff(c(y1,y2,y3,y4)) <= 0) ~ "1. nonincreasing",
    all(diff(c(y1,y2,y3,y4)) >= 0) ~ "1. nondecreasing",
    all(sign(diff(c(y1,y2,y3,y4))) == c(1,-1,1)) ~ "3. zig zag (inc)",
    all(sign(diff(c(y1,y2,y3,y4))) == c(-1,1,-1)) ~ "3. zig zag (dec)",
    y1 < y2 && y2 > y3 && y3 > y4 ~ "2. peak",
    y1 < y2 && y2 < y3 && y3 > y4 ~ "2. peak",
    y1 > y2 && y2 < y3 && y3 < y4 ~ "2. valley",
    y1 > y2 && y2 > y3 && y3 < y4 ~ "2. valley",
    all(sign(diff(c(y1,y2,y3,y4))) == c(1,0,-1)) ~ "2. hump (n)",
    all(sign(diff(c(y1,y2,y3,y4))) == c(-1,0,1)) ~ "2. hump (u)",
    TRUE ~ "other"
  )) %>% 
  group_by(part_c_type) %>% 
  mutate(count = n())

part_c_correct %>% 
  group_by(part_c_type) %>% 
  tally()

part_c_correct %>% 
  mutate(incdec_type = if_else(str_detect(incdec, "dec"), "decreasing somewhere", "nondecreasing")) %>% 
  group_by(incdec_type) %>% 
  tally()

```

```{r fig.height=6, fig.width=6}
part_c_correct %>% 
  group_by(part_c_type) %>% 
  slice_head(n = 1) %>% 
  mutate(userid = str_glue("{part_c_type} (n={count})")) %>% 
  plot_responses(title = "Task C: Families of correct responses")

ggsave("2020-stack-responses/FIG_task3_correct.pdf", units = "cm", width = 18)
```

Another way to look at it - answers are only correct if the function is non-injective, which is achieved either with a flat segment, or a change between increasing and decreasing (or both features).

```{r}
part_c_correct_features <- part_c_correct %>% 
  mutate(feature_analysis = case_when(
    str_detect(incdec, "flat") && !str_detect(incdec, "inc") ~ "monotone flat",
    str_detect(incdec, "flat") && !str_detect(incdec, "dec") ~ "monotone flat",
    !str_detect(incdec, "flat") ~ "no flat",
    str_detect(incdec, "flat") && str_detect(incdec, "inc") && str_detect(incdec, "dec") ~ "both",
    TRUE ~ "other"
  ))

part_c_correct_features %>% 
  group_by(feature_analysis) %>% 
  tally()
```

```{r}
part_c_correct_features %>% 
  filter(feature_analysis == "no flat") %>% 
  head(n = 25) %>% 
  plot_responses(title = "Families of correct responses")  + theme(panel.spacing = unit(0.2, "lines"))
```







```{r}
part_c_correct %>% 
  filter(part_c_type == "other") %>% 
  plot_responses(title = "Correct responses in the \"Other\" group")
```


#### Not a function

Most of those with an unidentified error had introduced vertical segments:

```{r fig.height=7, fig.width=8}
response_issues %>% 
  filter(part == "c", score == 0, nature_of_mistake == "") %>% 
  plot_responses(title = "Not a function")
```
Note - response 3576 is being plotted incorrectly here: the student actually reversed the order of the middle two points (`r (response_issues %>% filter(userid == 3576) %>% filter(part == "c"))$response`) so the graph would have looked like a "lightning bolt" shape to the student.

The remaining "not a function" responses are quite varied, failing to meet the required properties in different ways:

```{r fig.height=7, fig.width=8}
response_issues %>% 
  filter(part == "c", score == 0, example_type == "not a function", nature_of_mistake != "") %>% 
  plot_responses(title = "Not a function")
```

#### Partially correct

Many of the students gave examples that were not injective (as required) but also _not_ surjective. Among them, a common pattern was to give a function with image $[0,\frac12]$:

```{r fig.height=4, fig.width=8}
response_issues %>% 
  filter(part == "c", score == 0.5, nature_of_mistake == "image is [0,1/2]") %>% 
  plot_responses(title = "image is [0,1/2]")
```

Though many other students missed other parts of the image:

```{r fig.height=4, fig.width=8}
response_issues %>% 
  filter(part == "c", score == 0.5, nature_of_mistake == "image too small") %>% 
  plot_responses(title = "Image too small")
```

Another common error was to provide a surjective function, but one that was injective when it should not be:

```{r fig.height=4, fig.width=8}
response_issues %>% 
  filter(part == "c", score == 0.5, nature_of_mistake == "injective but should not be") %>% 
  plot_responses(title = "injective but should not be")
```

#### Incorrect

The remaining incorrect answers are quite diverse:

```{r fig.height=5, fig.width=8}
response_issues %>% 
  filter(part == "c", score == 0, example_type == "piecewise linear") %>% 
  plot_responses(title = "Misc incorrect")
```

Several of those are horizontal lines.







### (d) injective, not surjective, and passes through $(0.2, 0.8)$ and $(0.5, 0.5)$

```{r}
response_issues %>%
  filter(part == "d") %>%
  group_by(score, example_type, nature_of_mistake) %>%
  tally() %>%
  arrange(-score, example_type, -n) %>% 
  basic_kable() %>% 
  collapse_rows(columns = c(1:2), valign = "top")
```

#### Correct answers

Correct responses here are relatively constrained.

The most common correct answers fix the middle two points to the ones given in the task, and either have the first point below y=1 or the last point above y=0 (or both). We label these the "standard" answers.

A few students chose to use different locations for the middle two points, though still satisfying the conditions given in the task (labelled "nonstandard").

```{r}
part_d_correct <- response_issues %>% 
  filter(part == "d", score == 1) %>% 
  mutate(part_d_type = case_when(
    x2 != 0.2 || x3 != 0.5 ~ "nonstandard",
    y1 < 1 && y4 > 0 ~ "standard: both ends",
    y1 < 1 ~ "standard: top end",
    y4 > 0 ~ "standard: bottom end",
    TRUE ~ "other"
  )) %>% 
  group_by(part_d_type) %>% 
  mutate(count = n())

part_d_correct %>% 
  group_by(part_d_type) %>% 
  tally()

part_d_correct %>% 
  group_by(part_d_type) %>% 
  slice_head(n = 1) %>% 
  mutate(userid = str_glue("{part_d_type} (n={count})")) %>% 
  plot_responses(title = "Task D: Families of correct responses")

ggsave("2020-stack-responses/FIG_task4_correct.pdf", units = "cm", width = 18)
```

The "other" example here is actually incorrect (by somehow having the first point at $(0, 1.1)$) and the STACK grading is not picking this up.


#### Partially correct

Many of the students gave examples that were not injective (as required) but also _not_ surjective. Among them, a common pattern was to give a function with image $[0,\frac12]$:

```{r fig.height=4, fig.width=8}
response_issues %>% 
  filter(part == "c", score == 0.5, nature_of_mistake == "image is [0,1/2]") %>% 
  plot_responses(title = "image is [0,1/2]")
```

Though many other students missed other parts of the image:

```{r fig.height=4, fig.width=8}
response_issues %>% 
  filter(part == "c", score == 0.5, nature_of_mistake == "image too small") %>% 
  plot_responses(title = "Image too small")
```

Another common error was to provide a surjective function, but one that was injective when it should not be:

```{r fig.height=4, fig.width=8}
response_issues %>% 
  filter(part == "c", score == 0.5, nature_of_mistake == "injective but should not be") %>% 
  plot_responses(title = "injective but should not be")
```

#### Incorrect

As before, several students included vertical segments or made two points coincide:

```{r fig.height=7, fig.width=8}
response_issues %>% 
  filter(part == "d", score == 0, example_type == "not a function") %>% 
  plot_responses(title = "Not a function")
```

The most common class of incorrect responses had gaps in the domain:

```{r fig.height=5, fig.width=8}
response_issues %>% 
  filter(part == "d", score == 0, example_type == "piecewise linear", nature_of_mistake == "domain has gaps") %>% 
  plot_responses(title = "Misc incorrect")
```

The remaining incorrect answers are not very interesting:

```{r fig.height=5, fig.width=8}
response_issues %>% 
  filter(part == "d", score == 0, example_type == "piecewise linear", nature_of_mistake != "domain has gaps") %>% 
  plot_responses(title = "Misc incorrect")
```








