---
title: "Written responses - analysis of coding"
author: "George Kinnear"
date: "08/10/2021"
always_allow_html: true
output:
  html_document:
    df_print: paged
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)

# Tables
library(knitr)
library(kableExtra)
basic_kable = function(df) {
  df %>% 
    kable() %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}
rmarkdown::html_document(df_print = knitr::kable)
options(knitr.kable.NA = '')

# Set preferred styling
theme_set(theme_minimal())

# Compute IRR using Gwet's CRAN package:
library(irrCAC)
```

## Coding

```{r}
coders <- c("GK", "PI", "BD")

# read in all the data, from separate Excel workbooks
coding_raw <- tibble(coder = coders) %>% 
  mutate(data = map(coder, ~ readxl::read_excel(here::here("2021-written-responses", paste0("coding-", .x ,".xlsx"))))) %>% 
  unnest(cols = data)

coding_clean <- coding_raw %>% 
  # tidy up the contents
  mutate(across(c(correct, gives_equation), str_to_upper)) %>%
  mutate(across(c(example_type, nature_of_mistake), str_to_lower)) %>% 
  mutate(across(c(correct, gives_equation, example_type, nature_of_mistake), str_trim)) %>% 
  mutate(example_type = str_replace_all(example_type, 'quadratic \\(parabola\\)', "quadratic")) %>% 
  mutate(example_type = str_replace_all(example_type, 'picewise', "piecewise")) %>% 
  mutate(example_type = str_replace_all(example_type, 'other unclear', "other - unclear")) %>% 
  mutate(example_type = str_replace_all(example_type, 'other - no answer visible', "no answer visible")) %>% 
  mutate(example_type = str_replace_all(example_type, '^o$', "other")) %>% 
  mutate(example_type = str_replace_all(example_type, '–', "-")) %>% 
  mutate(nature_of_mistake = str_replace_all(nature_of_mistake, 'domain goes beyond', "domain exceeds")) %>% 
  mutate(nature_of_mistake = str_replace_all(nature_of_mistake, "domain too small|domain is too small", "domain has gaps")) %>% 
  mutate(nature_of_mistake = str_replace_all(nature_of_mistake, 'surjective and', "surjective but")) %>% 
  mutate(nature_of_mistake = str_replace_all(nature_of_mistake, '0, 1', "0,1")) %>% 
  mutate(nature_of_mistake = str_replace_all(nature_of_mistake, 'n/a', "")) %>% 
  mutate(nature_of_mistake = na_if(nature_of_mistake, "")) %>% 
  mutate(nature_of_mistake = case_when(
    part == "d" & nature_of_mistake == "surjective" ~ "surjective but should not be",
    TRUE ~ nature_of_mistake
  ))


# coding_gk <- readxl::read_excel(here::here("2021-written-responses", "coding-GK.xlsx"))
```


These entries do not use one of the agreed codes for `nature_of_mistake`:

```{r}
coding_clean %>% 
  mutate(
    nature_of_mistake = str_remove_all(nature_of_mistake, "undefined at a point|domain is \\[0,1/2\\]|domain has gaps|domain exceeds \\[0,1\\]"),
    nature_of_mistake = str_remove_all(nature_of_mistake, "image is \\[1/2,1\\]|surjective but should not be|image goes beyond \\[0,1\\]"),
    nature_of_mistake = str_remove_all(nature_of_mistake, "image too small|image too large but still a subset of \\[0,1\\]"),
    nature_of_mistake = str_remove_all(nature_of_mistake, "image is \\[0,1/2\\]"),
    nature_of_mistake = str_remove_all(nature_of_mistake, "does not pass through the required points|not injective|not a function|axis not labelled|injective but should not be|no answer visible"),
    nature_of_mistake = str_remove_all(nature_of_mistake, ";|n/a") %>% str_trim()
  ) %>% 
  filter(str_length(nature_of_mistake) > 0) %>% 
  select(coder, script, part, nature_of_mistake) %>% 
  basic_kable()
```

These entries do not use one of the agreed codes for `example_type`:

```{r}
coding_clean %>% 
  filter(!example_type %in% c("linear", "piecewise linear", "piecewise other", "quadratic", "cubic", "trig", "not a function", "no answer visible")) %>% 
  filter(!str_detect(example_type, "other - ")) %>% 
  select(coder, script, part, example_type) %>% 
  basic_kable()
```


We coded `r coding_clean %>% select(script) %>% n_distinct()` scripts. These were divided between coders, with some overlap.

```{r}
coding_clean %>% 
  select(coder, script) %>% 
  distinct() %>% 
  group_by(coder) %>% 
  tally() %>% 
  basic_kable()
```

### Reliability

```{r}
# pick out the scripts that were double-coded
double_coding <- coding_clean %>% 
  semi_join(
    coding_clean %>% 
      group_by(script, part) %>% 
      tally() %>% 
      filter(n > 1) %>% 
      select(script),
    by = "script"
  )

# put each coder's work in separate columns
double_coded_vars <- c("correct", "gives_equation", "example_type", "nature_of_mistake", "notes")
double_coding_wide <- double_coding %>% 
  pivot_longer(
    cols = all_of(double_coded_vars),
    names_to = "var",
    values_to = "value"
  ) %>% 
  pivot_wider(
    names_from = c(coder, var),
    values_from = "value",
    names_sep = "__"
  )
```

A total of `r double_coding_wide %>% select(script) %>% n_distinct()` scripts were coded by more than one coder.

For each of the variables of interest, we construct a table which has a column for each coder's input for that variable. We then use the `irrCAC` package to compute various reliability measures:

```{r}
# helper function to compute multiple IRR stats at once
IRR_coeffs <- function(cal) {
  # remove any columns with all NA
  cal = cal %>% select_if(function(x) !(all(is.na(x)) | all(x=="")))
  # use irrCAC to find the values
  gwet = irrCAC::gwet.ac1.raw(cal)
  krip = irrCAC::krippen.alpha.raw(cal)
  pa = list("coeff.name" = "Percent agreement", "coeff.val" = gwet$est[["pa"]], "conf.int" = "")
  return(bind_rows(as_tibble(gwet$est),as_tibble(krip$est),as_tibble(pa)) %>% select(names(pa)))
}

# compute the IRR stats for each of the variables of interest
tibble(variable = double_coded_vars) %>%
  filter(variable != "notes") %>% 
  mutate(
    irr_stats = map(
      variable,
      ~ double_coding_wide %>%
        select(contains(.x)) %>%
        janitor::remove_empty("rows") %>%
        IRR_coeffs()
    )
  ) %>% 
  unnest(cols = irr_stats) %>% 
  basic_kable() %>% 
  collapse_rows(columns = 1, valign = "top")


```

#### Disagreements

```{r}
agreement <- function(cols) {
  return(tibble(cols) %>% drop_na() %>% n_distinct() <= 1)
}

double_coding_wide %>% 
  rowwise() %>% 
  mutate(agreement_flag = agreement(c_across(contains("correct")))) %>% 
  filter(agreement_flag == FALSE) %>% 
  select(script, part, contains("correct")) %>% 
  basic_kable()

double_coding_wide %>% 
  rowwise() %>% 
  mutate(agreement_flag = agreement(c_across(contains("gives_equation")))) %>% 
  filter(agreement_flag == FALSE) %>% 
  select(script, part, contains("gives_equation")) %>% 
  basic_kable()

example_type_disagreements <- double_coding_wide %>% 
  rowwise() %>% 
  mutate(agreement_flag = agreement(c_across(contains("example_type")))) %>% 
  filter(agreement_flag == FALSE) %>% 
  select(script, part, contains("example_type"))

example_type_disagreements %>% 
  basic_kable()


nature_of_mistake_disagreements <- double_coding_wide %>% 
  rowwise() %>% 
  mutate(agreement_flag = agreement(c_across(contains("nature_of_mistake")))) %>% 
  filter(agreement_flag == FALSE) %>% 
  select(script, part, contains("nature_of_mistake"))

# nature_of_mistake_disagreements %>% 
#   basic_kable()
```

#### Summary of the disagreements

example_type:

```{r}
example_type_disagreements %>% 
  group_by(GK__example_type, PI__example_type, BD__example_type) %>% 
  summarise(
    n = n(),
    scripts = paste(paste0(script, part), collapse = ", "),
    .groups = "drop"
  ) %>% 
  arrange(-n) %>% 
  basic_kable()
```


nature_of_mistake:

```{r}
nature_of_mistake_disagreements %>% 
  group_by(GK__nature_of_mistake, PI__nature_of_mistake, BD__nature_of_mistake) %>% 
  summarise(
    n = n(),
    scripts = paste(paste0(script, part), collapse = ", "),
    .groups = "drop"
  ) %>% 
  arrange(-n) %>% 
  basic_kable()

```

## Resolving disagreements

The final agreed codings are saved in the following:

* scripts 1-125: GK
* scripts 126-208: PI
* scripts 209-333: BD

```{r}
coding_final <- coding_clean %>% 
  group_by(script, part) %>% 
  arrange(coder) %>% 
  sample_n(size = 1)

coding_final <- coding_clean %>% 
  mutate(
    final_code = case_when(
      script <= 125 & coder == "GK" ~ TRUE,
      script >= 209 & coder == "BD" ~ TRUE,
      script > 125 & script < 209 & coder == "PI" ~ TRUE,
      TRUE ~ FALSE
    )
  ) %>% 
  filter(final_code) %>% 
  select(-final_code)

coding_final %>% 
  write_csv("coding-final.csv")
```



```{r}
coding_final %>% 
  group_by(part, correct) %>% 
  tally() %>% 
  ggplot(aes(x = part, y = n, group = correct, fill = correct)) +
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_viridis_d(option = "plasma", end = 0.8) +
  labs(title = "Number of correct answers to each part")

coding_final %>%
  # correct only when the score is 1, incorrect otherwise
  mutate(correct = if_else(correct == "Y", "Correct", "Incorrect")) %>%
  # for a couple of students we couldn't decide correctness, so map this to "incorrect"
  mutate(correct = replace_na(correct, "Incorrect")) %>% 
  #filter(!is.na(correct)) %>% 
  janitor::tabyl(part, correct) %>%
  janitor::adorn_totals("col") %>%
  janitor::adorn_percentages() %>%
  janitor::adorn_pct_formatting(digits = 0) %>%
  janitor::adorn_ns(position = "front") %>% 
  basic_kable()
```

```{r}
coding_final %>% 
  group_by(part, correct, nature_of_mistake) %>% 
  tally() %>% 
  arrange(part, desc(correct), -n) %>% 
  basic_kable() %>% 
  collapse_rows(columns = 1:2, valign = "top")
```

## Types of example

```{r}
# intended categories, in manually set order
example_type_list <- c("linear", "cubic", "quadratic", "piecewise linear", "other", "not a function", "no answer visible")
```


```{r}
# coding_clean %>% 
#   group_by(coder, example_type) %>% 
#   tally() %>% 
#   basic_kable()

coding_clean %>% 
  janitor::tabyl(example_type, coder) %>% 
  janitor::adorn_totals(where = "both") %>% 
  basic_kable()
```

```{r}
coding_final_plotdat <- coding_final %>% 
  mutate(example_type = case_when(
    str_detect(example_type, "other|1/x|ln\\(x\\)") ~ "other",
    str_detect(example_type, "curve|exp|hyp|trig|\\?|-") ~ "other",
    str_detect(example_type, "wise") ~ "piecewise linear",
    str_detect(example_type, "cubic") ~ "cubic",
    example_type == "p" ~ "other",
    TRUE ~ example_type
  ))

coding_final_plotdat %>% 
  group_by(part, example_type) %>% 
  tally() %>% 
  mutate(example_type = fct_relevel(example_type, example_type_list)) %>% 
  ggplot(aes(x = part, y = n, group = example_type, fill = example_type)) +
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_viridis_d("Example type", option = "plasma", end = 0.8, direction = -1) +
  labs(title = "Range of examples given for each part")

# coding_clean %>% 
#   group_by(part, correct, example_type) %>% 
#   tally() %>% 
#   ungroup() %>% 
#   filter(correct %in% c("Y", "N")) %>% 
#   mutate(correct = ifelse(correct == "Y", "Correct", "Incorrect")) %>% 
#   mutate(example_type = fct_relevel(example_type, example_type_list)) %>% 
#   ggplot(aes(x = part, y = n, group = example_type, fill = example_type)) +
#   geom_bar(position = "stack", stat = "identity") +
#   scale_fill_viridis_d("Example type", option = "plasma", end = 0.8, direction = -1) +
#   labs(title = "Range of examples given for each part") +
#   coord_flip() +
#   facet_grid(cols = vars(correct))

# https://bookdown.org/lyzhang10/lzhang_r_tips_book/how-to-plot-data.html#creating-back-to-back-bar-charts
back_to_back_dat <- coding_final_plotdat %>% 
  group_by(part, correct, example_type) %>% 
  filter(!is.na(example_type)) %>% 
  tally() %>% 
  ungroup() %>% 
  filter(correct %in% c("Y", "N")) %>% 
  mutate(correct = ifelse(correct == "Y", "Correct", "Incorrect")) %>% 
  mutate(correct = fct_relevel(correct, "Incorrect")) %>% 
  mutate(example_type = fct_relevel(example_type, example_type_list)) %>% 
  mutate(signed_n = if_else(correct == "Correct", n, -n))

back_to_back_dat %>% 
  mutate(part = fct_rev(part)) %>% 
  ggplot(aes(x = part, y = signed_n, group = example_type, fill = example_type)) +
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_viridis_d("Example type", option = "plasma", end = 0.8, direction = -1) +
  scale_y_continuous("Number of students", labels = abs, breaks = seq(-350, 350, 50)) +
  geom_hline(yintercept = 0) +
  labs(title = "Range of examples given for each part", x = "") +
  coord_flip() +
  annotate("text", x = 4.8, y = 25, label = "Correct", fontface = "bold", hjust = "left", vjust = "top") +
  annotate("text", x = 4.8, y = -25, label = "Incorrect", fontface = "bold", hjust = "right", vjust = "top")


```


```{r}
coding_final_plotdat %>% 
  filter(!is.na(example_type), !is.na(correct)) %>% 
  filter(correct == "Y") %>%
  janitor::tabyl(example_type, part, show_missing_levels = FALSE) %>%
  janitor::adorn_totals("both") %>%
  janitor::adorn_percentages(denominator = "col") %>%
  janitor::adorn_pct_formatting(digits = 0) %>%
  janitor::adorn_ns(position = "front") %>% 
  basic_kable()
```


# Analysis of each part

## Part (a)

### Incorrect


```{r}
coding_final %>% 
  filter(part == "a", correct == "N") %>% 
  janitor::tabyl(nature_of_mistake) %>% 
  arrange(-n) %>%
  janitor::adorn_pct_formatting() %>% 
  janitor::adorn_totals("row") %>% 
  basic_kable() %>% 
  collapse_rows(columns = 1:2, valign = "top")
```
```{r}
coding_final %>% 
  filter(part == "a", correct == "N", str_detect(nature_of_mistake, "surjective")) %>% 
  select(coder, script, nature_of_mistake)
```

```{r}
coding_final %>% 
  filter(part == "a", correct == "N", str_detect(nature_of_mistake, "not a function")) %>% 
  select(coder, script, nature_of_mistake)
```

## Part (b)

### Incorrect



```{r}
coding_final %>% 
  filter(part == "b", correct == "N") %>% 
  janitor::tabyl(nature_of_mistake) %>% 
  arrange(-n) %>%
  janitor::adorn_pct_formatting() %>% 
  janitor::adorn_totals("row") %>% 
  basic_kable() %>% 
  collapse_rows(columns = 1:2, valign = "top")
```

```{r}
coding_final %>% 
  filter(part == "b", correct == "N", str_detect(nature_of_mistake, "image")) %>% 
  select(coder, script, nature_of_mistake) %>% 
  arrange(nature_of_mistake, script)
```


```{r}
coding_final %>% 
  filter(part == "b", correct == "N", str_detect(nature_of_mistake, "surjective")) %>% 
  select(coder, script, nature_of_mistake)
```
For students who made a mistake with the image in (b), what did they do in (a)?

```{r}
coding_final %>% 
  filter(part == "a") %>% 
  semi_join(
    coding_final %>% 
      filter(part == "b", correct == "N", str_detect(nature_of_mistake, "image too large|image goes beyond|surjective")) %>% 
      select(script),
    by = "script"
  ) %>% 
  select(coder, script, correct, nature_of_mistake) %>% 
  arrange(correct, script)

```


```{r}
coding_final %>% 
  filter(part == "b", correct == "N", !str_detect(nature_of_mistake, "image")) %>% 
  select(coder, script, nature_of_mistake) %>% 
  arrange(nature_of_mistake, script)
```















