---
title: "Interview responses - analysis of example chains"
author: "George Kinnear"
date: "2023-06-21"
always_allow_html: true
output:
  html_document:
    df_print: paged
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)

# Tables
library(gt)
library(knitr)
library(kableExtra)
basic_kable = function(df) {
  df %>% 
    kable() %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}
rmarkdown::html_document(df_print = knitr::kable)
options(knitr.kable.NA = '')

# Set preferred styling
theme_set(theme_minimal())
```

## Data

```{r}
chains_data <- read_csv("example-chain-details.csv", show_col_types = FALSE) %>% 
  janitor::clean_names() %>% 
  mutate(group = if_else(str_detect(participant, "S"), "e-assessment", "written"), .before = "participant") %>% 
  # clean up the Transformation strategy %>% 
  mutate(strategy = if_else(strategy == "TRP", "TR", strategy))

chains_data %>% 
  basic_kable()
```

## Counting chains

```{r}
chains_data %>% 
  group_by(group, participant, task) %>% 
  tally(name = "num_steps") %>% 
  group_by(group) %>% 
  tally(name = "num_chains") %>% 
  janitor::adorn_totals() %>% 
  basic_kable()
```

## Correctness


```{r}
chains_scored <- chains_data %>% 
  # add final_correct column to record whether the chain was eventually correct
  left_join(
    chains_data %>% 
      select(participant, task, example_num, correct) %>% 
      group_by(participant, task) %>% 
      slice_max(order_by = example_num, n = 1) %>% 
      select(-example_num) %>% 
      rename(final_correct = correct),
    by = c("participant", "task")
  ) %>% 
  # decide on the "correctness" score for each chain
  group_by(group, participant, task) %>% 
  mutate(had_prompt = sum(validation == "prompted", na.rm = TRUE) > 0) %>% 
  mutate(correctness = case_when(
    had_prompt == FALSE ~ paste0("", final_correct),
    had_prompt == TRUE & final_correct == 1 ~ "1 - prompted",
    had_prompt == TRUE & final_correct == 0 ~ "0",
  ))

chains_scored %>% 
  group_by(group, participant, task) %>% 
  summarise(correctness = max(correctness), .groups = "drop") %>% 
  group_by(correctness) %>% 
  tally(name = "num_chains") %>% 
  janitor::adorn_totals() %>% 
  basic_kable()
```

## Chain endings

```{r}
chains_scored %>% 
  group_by(group, participant, task) %>% 
  slice_max(example_num, n = 1) %>% 
  group_by(terminal_strategy = strategy) %>% 
  tally()
```

In four of these cases, students generated a correct example at the end of that chain without
prompts, while in a further 13 cases the final example was correct but produced only
after prompts by the interviewer.
The remaining five cases ended with an incorrect solution

```{r}
chains_scored %>% 
  group_by(group, participant, task) %>% 
  slice_max(example_num, n = 1) %>% 
  group_by(terminal_strategy = strategy, correctness) %>% 
  filter(terminal_strategy == "TR") %>% 
  tally()
```

```{r}
chains_scored %>% 
  group_by(group, participant, task) %>% 
  # all steps based on T&E
  filter(sum(strategy == "T&E") == n())
```

## Chain beginnings

```{r}
chains_scored %>% 
  group_by(group, participant, task) %>% 
  slice_min(example_num, n = 1) %>% 
  group_by(initial_strategy = strategy) %>% 
  tally()
```

Focusing on the chains that start with DA:

```{r}
chains_scored %>% 
  group_by(group, participant, task) %>% 
  slice_min(example_num, n = 1) %>% 
  group_by(initial_strategy = strategy, correctness) %>% 
  filter(initial_strategy == "DA") %>% 
  tally()
```

Looking in more detail at these:

```{r}
da_first_attempts <- chains_scored %>% 
  group_by(group, participant, task) %>% 
  mutate(uses_DA_first = sum(strategy == "DA" & example_num == 1)) %>% 
  filter(uses_DA_first > 0)

da_first_attempts
```



```{r}
da_first_attempts %>% 
  ggplot(aes(x = 1, y = -(example_num-1), label = strategy, colour = correctness)) +
  geom_segment(aes(xend = 1, y = -0.2-(example_num-2)*(if_else(example_num == 1, 0, 1)), yend = -(example_num-1)+0.2), arrow = arrow(length = unit(0.25, "cm"), type = "closed"), size = 0.8) +
  geom_label() +
  facet_wrap(vars(participant, task)) +
  theme_void()
```


## Strategy transitions

```{r}
chains_data %>% 
  group_by(group, participant, task) %>% 
  mutate(next_strategy = lead(strategy)) %>% 
  ungroup() %>% 
  select(strategy, next_strategy) %>% 
  filter(!is.na(next_strategy)) %>% 
  group_by(strategy, next_strategy) %>% 
  tally()
```

